### 2020-06-16 paper/paper.tex
Add paper

\documentclass[letterpaper]{article}
\usepackage{aaai}
\usepackage{times}
\usepackage{helvet}
\usepackage{courier}
\usepackage{hyperref}

\frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
    /Title (Sequence-to-sequence Architecture Using BERT)
    /Author (Claudio Scheer, Fernando Possebon)
}
\setcounter{secnumdepth}{0}
\begin{document}
% The file aaai.sty is the style file for AAAI Press 
% proceedings, working notes, and technical reports.
%
\title{Sequence-to-sequence Architecture\\Using BERT}
\author{Claudio Scheer \and Fernando Possebon\\
    Pontifical Catholic University of Rio Grande do Sul - PUCRS\\
    claudio.scheer@edu.pucrs.br,
    claudio.scheer@edu.pucrs.br
}

\maketitle

\begin{abstract}
\begin{quote}
Abstract.
\end{quote}
\end{abstract}

\noindent Introduction.

\section{Related works}
Related works.

\section{Deep Learning}

\subsection{Sequence-to-sequence}

The encoder-decoder architecture was initially proposed by \cite{DBLP:journals/corr/ChoMGBSB14}. Although simple, the idea was powerful: use a recurrent network to encode the input data and a decoder to transform the encoded input into the desirable output.

\cite{DBLP:journals/corr/Graves13} - Generating sequences with LSTM

\cite{DBLP:journals/corr/BahdanauCB14} - Proposed attention

\cite{DBLP:journals/corr/VaswaniSPUJGKP17} - Attention is all you need

\subsection{BERT}

\cite{DBLP:journals/corr/abs-1810-04805} - BERT

\subsection{Sequence-to-sequence BERT}

Similarly to the original sequence-to-sequence model using a recurrent neural network, the model discussed in this paper uses two BERT neural network: one neural network to encode the input and another to decode the input encoded.

\section{Dataset}

As we focused our project on automatic email response, we used The Enron Email Dataset\footnote{\href{https://www.kaggle.com/wcukierski/enron-email-dataset}{https://www.kaggle.com/wcukierski/enron-email-dataset}} to train our model. The dataset contains only the raw data from the emails. Therefore, we created a parser\footnote{\href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{https://www.kaggle.com/claudioscheer/extract-reply-emails}} to extract the email and the replies from each email.

To identify whether an email has a reply or not, we look for emails that contain the string \texttt{-----Original Message-----}. After filtering only emails with non-empty replies, we parse those emails in an input sequence (the original email) and in the target sequence (the reply email). The entire extraction was done automatically, that is, we did not manually extract or adjust any input.

The original dataset contains 517,401 raw emails. After parsing the raw dataset, we created a dataset with 110,205 input and target pairs. Not all pairs were parsed correctly. In the parsed dataset, 8,368 pairs have specifics patterns. As this data does not represent a large part of the dataset, we trained the dataset with this "wrong" data.

\bibliographystyle{aaai}
\bibliography{references}

\end{document}

### 2020-06-16 paper/paper.tex
Update paper

@@
     /Title (Sequence-to-sequence Architecture Using BERT)
-    /Author (Claudio Scheer, Fernando Possebon)
+    /Author (Claudio Scheer, José Fernando Possebon)
 }
@@
 \title{Sequence-to-sequence Architecture\\Using BERT}
-\author{Claudio Scheer \and Fernando Possebon\\
+\author{Claudio Scheer \and José Fernando Possebon\\
     Pontifical Catholic University of Rio Grande do Sul - PUCRS\\
     claudio.scheer@edu.pucrs.br,
-    claudio.scheer@edu.pucrs.br
+    jose.possebon@edu.pucrs.br
 }
@@
 
+In this section, we will discuss the sequence-to-sequence model using recurrent neural networks and transformers. Also, in a nutshell, we discuss how a BERT model works.
+
 \subsection{Sequence-to-sequence}
@@
 The encoder-decoder architecture was initially proposed by \cite{DBLP:journals/corr/ChoMGBSB14}.
-Although simple, the idea was powerful: use a recurrent network to encode the input data and a decoder to transform the encoded input into the desirable output.
+Although simple, the idea is powerful: use a recurrent neural network to encode the input data and a recurrent neural network to decode the encoded input into the desirable output.
+Two neural networks are trained.
 
@@
 
-\subsection{Sequence-to-sequence BERT}
-
 Similarly to the original sequence-to-sequence model using a recurrent neural network, the model discussed in this paper uses two BERT neural network: one neural network to encode the input and another to decode the input encoded.
@@
 
-As we focused our project on automatic email response, we used The Enron Email Dataset\footnote{\href{https://www.kaggle.com/wcukierski/enron-email-dataset}{https://www.kaggle.com/wcukierski/enron-email-dataset}} to train our model.
-The dataset contains only the raw data from the emails.
+As we focused our project on automatic email reply, we used The Enron Email Dataset\footnote{\href{https://www.kaggle.com/wcukierski/enron-email-dataset}{https://www.kaggle.com/wcukierski/enron-email-dataset}} to train our model.
+The dataset contains only the raw data of the emails.
 Therefore, we created a parser\footnote{\href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{https://www.kaggle.com/claudioscheer/extract-reply-emails}} to extract the email and the replies from each email.
@@
 After filtering only emails with non-empty replies, we parse those emails in an input sequence (the original email) and in the target sequence (the reply email).
-The entire extraction was done automatically, that is, we did not manually extract or adjust any input.
+The entire extraction was done automatically, that is, we did not manually extract or adjust any email.
 
-The original dataset contains 517,401 raw emails.
-After parsing the raw dataset, we created a dataset with 110,205 input and target pairs.
-Not all pairs were parsed correctly.
-In the parsed dataset, 8,368 pairs have specifics patterns.
-As this data does not represent a large part of the dataset, we trained the dataset with this "wrong" data.
+We used two libraries to parse the dataset: \texttt{talon}\footnote{\href{https://github.com/mailgun/talon}{https://github.com/mailgun/talon}}, provided by Mailgun, and \texttt{email}, provided by Python.
+The \texttt{email} package returns the email body with the entire thread.
+To extract only the last reply from an email thread, we use the \texttt{talon} package.
+
+The original dataset contains 517,401 raw emails. After parsing the raw dataset, we created a dataset with 110,205 input and target pairs.
+
+In the parsed dataset, we have 8,368 pairs with specifics email and reply patterns. Since these pairs do not represent a large part of the dataset, we trained the dataset with this "wrong" data.
 

### 2020-06-16 src/seq2seq/load_model.py
Change sequence size to 256

@@ -12,9 +12,9 @@ transformers_logger = logging.getLogger("transformers")
 transformers_logger.setLevel(logging.WARNING)
 
 model_args = {
-    "eval_batch_size": 2,
-    "max_seq_length": 128,
-    "max_length": 128,
+    "eval_batch_size": 1,
+    "max_seq_length": 256,
+    "max_length": 256,
     "num_beams": 3,
     "early_stopping": False,
 }

### 2020-06-16 src/seq2seq/main.py

@@ -16,13 +16,10 @@ train_df.dropna(subset=["input_text", "target_text"], inplace=True)
 model_args = {
     "fp16": False,
     "overwrite_output_dir": True,
-    "max_seq_length": 512,
-    "train_batch_size": 2,
-    "eval_batch_size": 1,
+    "max_seq_length": 256,
+    "train_batch_size": 8,
     "num_train_epochs": 16,
-    "max_length": 512,
-    "num_beams": 3,
-    "early_stopping": False,
+    "max_length": 256,
     "learning_rate": 1e-4,
     "save_eval_checkpoints": False,
     "save_model_every_epoch": False,

### 2020-06-16 src/seq2seq/main.py
Change dataset path

@@ -9,7 +9,7 @@ transformers_logger = logging.getLogger("transformers")
 transformers_logger.setLevel(logging.WARNING)
 
 file_path = os.path.dirname(os.path.abspath(__file__))
-train_df = pd.read_csv(os.path.join(file_path, "../../dataset/input-target.csv"))
+train_df = pd.read_csv(os.path.join(file_path, "../../dataset/input-target-256-dev.csv"))
 train_df.drop(train_df.columns[[0]], axis=1, inplace=True)
 train_df.dropna(subset=["input_text", "target_text"], inplace=True)
 

### 2020-06-17 src/seq2seq/lib/global_args.py
Update scripts according to simpletransformers

@@ -16,13 +16,14 @@ global_args = {
     "encoding": None,
     "eval_batch_size": 8,
     "evaluate_during_training": False,
+    "evaluate_during_training_silent": True,
     "evaluate_during_training_steps": 2000,
     "evaluate_during_training_verbose": False,
-    "evaluate_generated_text": False,
     "fp16": True,
     "fp16_opt_level": "O1",
     "gradient_accumulation_steps": 1,
     "learning_rate": 4e-5,
+    "local_rank": -1,
     "logging_steps": 50,
     "manual_seed": None,
     "max_grad_norm": 1.0,
@@ -46,7 +47,7 @@ global_args = {
     "train_batch_size": 8,
     "use_cached_eval_features": False,
     "use_early_stopping": False,
-    "use_multiprocessing": False,
+    "use_multiprocessing": True,
     "wandb_kwargs": {},
     "wandb_project": None,
     "warmup_ratio": 0.06,

### 2020-06-17 src/seq2seq/lib/seq2seq_model.py

@@ -36,6 +36,9 @@ from transformers import (
     ElectraConfig,
     ElectraModel,
     ElectraTokenizer,
+    LongformerConfig,
+    LongformerModel,
+    LongformerTokenizer,
     PreTrainedModel,
     PreTrainedTokenizer,
     RobertaConfig,
@@ -60,13 +63,14 @@ logger = logging.getLogger(__name__)
 
 MODEL_CLASSES = {
     "auto": (AutoConfig, AutoModel, AutoTokenizer),
-    "bert": (BertConfig, BertModel, BertTokenizer),
-    "roberta": (RobertaConfig, RobertaModel, RobertaTokenizer),
-    "distilbert": (DistilBertConfig, DistilBertModel, DistilBertTokenizer),
-    "camembert": (CamembertConfig, CamembertModel, CamembertTokenizer),
-    "electra": (ElectraConfig, ElectraModel, ElectraTokenizer),
     "bart": (BartConfig, BartForConditionalGeneration, BartTokenizer),
+    "bert": (BertConfig, BertModel, BertTokenizer),
+    "camembert": (CamembertConfig, CamembertModel, CamembertTokenizer),
+    "distilbert": (DistilBertConfig, DistilBertModel, DistilBertTokenizer),
+    "electra": (ElectraConfig, ElectraModel, ElectraTokenizer),
+    "longformer": (LongformerConfig, LongformerModel, LongformerTokenizer),
     "marian": (MarianConfig, MarianMTModel, MarianTokenizer),
+    "roberta": (RobertaConfig, RobertaModel, RobertaTokenizer),
 }
 
 
@@ -109,13 +113,16 @@ class Seq2SeqModel:
         self.args = {
             "dataset_class": None,
             "do_sample": False,
-            "max_steps": -1,
-            "evaluate_generated_text": False,
-            "num_beams": 1,
-            "max_length": 20,
-            "repetition_penalty": 1.0,
-            "length_penalty": 2.0,
             "early_stopping": True,
+            "evaluate_generated_text": False,
+            "length_penalty": 2.0,
+            "max_length": 20,
+            "max_steps": -1,
+            "num_beams": 1,
+            "num_return_sequences": 1,
+            "repetition_penalty": 1.0,
+            "top_k": None,
+            "top_p": None,
         }
 
         self.args.update(global_args)
@@ -417,7 +424,7 @@ class Seq2SeqModel:
 
[…]

### 2020-06-17 src/seq2seq/lib/seq2seq_utils.py

@@ -19,7 +19,7 @@ logger = logging.getLogger(__name__)
 def preprocess_data(data):
     input_text, target_text, encoder_tokenizer, decoder_tokenizer, args = data
 
-    input_text = encoder_tokenizer.encode(input_text, max_length=args["max_seq_length"], pad_to_max_length=True, return_tensors="pt")
+    input_text = encoder_tokenizer.encode(input_text, max_length=args["max_seq_length"], pad_to_max_length=True, return_tensors="pt",)
 
     target_text = decoder_tokenizer.encode(target_text, max_length=args["max_seq_length"], pad_to_max_length=True, return_tensors="pt")
     return (torch.flatten(input_text), torch.flatten(target_text))

### 2020-06-17 src/seq2seq/load_model.py

@@ -12,11 +12,19 @@ transformers_logger = logging.getLogger("transformers")
 transformers_logger.setLevel(logging.WARNING)
 
 model_args = {
-    "eval_batch_size": 1,
+    "fp16": False,
+    "overwrite_output_dir": True,
     "max_seq_length": 256,
+    "train_batch_size": 16,
+    "num_train_epochs": 64,
     "max_length": 256,
-    "num_beams": 3,
-    "early_stopping": False,
+    "learning_rate": 1e-4,
+    "save_eval_checkpoints": False,
+    "save_model_every_epoch": False,
+    "save_best_model": False,
+    "save_steps": 100000,
+    "num_beams": 5,
+    "gradient_accumulation_steps": 1,
 }
 
 model = Seq2SeqModel(encoder_decoder_type="bert", encoder_decoder_name="outputs", args=model_args)

### 2020-06-17 src/seq2seq/main.py

@@ -17,13 +17,15 @@ model_args = {
     "fp16": False,
     "overwrite_output_dir": True,
     "max_seq_length": 256,
-    "train_batch_size": 8,
-    "num_train_epochs": 16,
+    "train_batch_size": 16,
+    "num_train_epochs": 64,
     "max_length": 256,
     "learning_rate": 1e-4,
     "save_eval_checkpoints": False,
     "save_model_every_epoch": False,
     "save_best_model": False,
+    "save_steps": 100000,
+    "num_beams": 5,
     "gradient_accumulation_steps": 1,
 }
 

### 2020-06-17 src/seq2seq/load_model.py
Update args

@@ -15,8 +15,8 @@ model_args = {
     "fp16": False,
     "overwrite_output_dir": True,
     "max_seq_length": 256,
-    "train_batch_size": 16,
-    "num_train_epochs": 64,
+    "train_batch_size": 8,
+    "num_train_epochs": 32,
     "max_length": 256,
     "learning_rate": 1e-4,
     "save_eval_checkpoints": False,

### 2020-06-17 src/seq2seq/main.py

@@ -17,8 +17,8 @@ model_args = {
     "fp16": False,
     "overwrite_output_dir": True,
     "max_seq_length": 256,
-    "train_batch_size": 16,
-    "num_train_epochs": 64,
+    "train_batch_size": 8,
+    "num_train_epochs": 32,
     "max_length": 256,
     "learning_rate": 1e-4,
     "save_eval_checkpoints": False,

### 2020-06-17 src/seq2seq/load_model.py
Load model based on saved args

@@ -11,21 +11,5 @@ logging.basicConfig(level=logging.INFO)
 transformers_logger = logging.getLogger("transformers")
 transformers_logger.setLevel(logging.WARNING)
 
-model_args = {
-    "fp16": False,
-    "overwrite_output_dir": True,
-    "max_seq_length": 256,
-    "train_batch_size": 8,
-    "num_train_epochs": 32,
-    "max_length": 256,
-    "learning_rate": 1e-4,
-    "save_eval_checkpoints": False,
-    "save_model_every_epoch": False,
-    "save_best_model": False,
-    "save_steps": 100000,
-    "num_beams": 5,
-    "gradient_accumulation_steps": 1,
-}
-
-model = Seq2SeqModel(encoder_decoder_type="bert", encoder_decoder_name="outputs", args=model_args)
+model = Seq2SeqModel(encoder_decoder_type="bert", encoder_decoder_name="outputs")
 print(model.predict([sys.argv[1]]))

### 2020-06-17 src/seq2seq/main.py
use_multiprocessing False

@@ -27,6 +27,7 @@ model_args = {
     "save_steps": 100000,
     "num_beams": 5,
     "gradient_accumulation_steps": 1,
+    "use_multiprocessing": False,
 }
 
 model = Seq2SeqModel(encoder_type="bert", encoder_name="bert-base-cased", decoder_name="bert-base-cased", args=model_args)

### 2020-06-17 src/seq2seq/main.py
save_model_every_epoch True

@@ -22,7 +22,7 @@ model_args = {
     "max_length": 256,
     "learning_rate": 1e-4,
     "save_eval_checkpoints": False,
-    "save_model_every_epoch": False,
+    "save_model_every_epoch": True,
     "save_best_model": False,
     "save_steps": 100000,
     "num_beams": 5,

### 2020-06-22 slides/slides.tex
Add slides

\documentclass{beamer}
\usepackage[utf8]{inputenc}

\usepackage{utopia} %font utopia imported

\usetheme{Madrid}
\usecolortheme{default}

%------------------------------------------------------------
%This block of code defines the information to appear in the
%Title page
\title[About Beamer] %optional
{About the Beamer class in presentation making}

\subtitle{A short story}

\author[Arthur, Doe] % (optional)
{A.~B.~Arthur\inst{1} \and J.~Doe\inst{2}}

\institute[VFU] % (optional)
{
  \inst{1}%
  Faculty of Physics\\
  Very Famous University
  \and
  \inst{2}%
  Faculty of Chemistry\\
  Very Famous University
}

\date[VLC 2014] % (optional)
{Very Large Conference, April 2014}

%End of title page configuration block
%------------------------------------------------------------

%------------------------------------------------------------
%The next block of commands puts the table of contents at the 
%beginning of each section and highlights the current section:

\AtBeginSection[]
{
  \begin{frame}
    \frametitle{Table of Contents}
    \tableofcontents[currentsection]
  \end{frame}
}
%------------------------------------------------------------

\begin{document}

%The next statement creates the title page.
\frame{\titlepage}

%---------------------------------------------------------
%This block of code is for the table of contents after
%the title page
\begin{frame}
\frametitle{Table of Contents}
\tableofcontents
\end{frame}
%---------------------------------------------------------

\section{First section}

%---------------------------------------------------------
%Changing visivility of the text
\begin{frame}
\frametitle{Sample frame title}
This is a text in second frame. For the sake of showing an example.

\begin{itemize}
    \item<1-> Text visible on slide 1
    \item<2-> Text visible on slide 2
    \item<3> Text visible on slides 3
    \item<4-> Text visible on slide 4
\end{itemize}
\end{frame}

%---------------------------------------------------------

%---------------------------------------------------------
%Example of the \pause command
\begin{frame}
In this slide \pause

the text will be partially visible \pause

And finally everything will be there
\end{frame}
%---------------------------------------------------------

\section{Second section}

%---------------------------------------------------------
%Highlighting text
\begin{frame}
\frametitle{Sample frame title}

In this slide, some important text will be
\alert{highlighted} because it's important.
Please, don't abuse it.

\begin{block}{Remark}
Sample text
\end{block}

\begin{alertblock}{Important theorem}
Sample text in red box
\end{alertblock}

\begin{examples}
Sample text in green box. The title of the block is ``Examples".
\end{examples}
\end{frame}
%---------------------------------------------------------

%---------------------------------------------------------
%Two columns
\begin{frame}
\frametitle{Two-column slide}

\begin{columns}

\column{0.5\textwidth}
This is a text in first column.
$$E=mc^2$$
\begin{itemize}
\item First item
\item Second item
\end{itemize}

\column{0.5\textwidth}
This text will be in the second column
and on a second tought this is a nice looking
layout in some cases.
\end{columns}
\end{frame}
%---------------------------------------------------------

\end{document}

### 2020-06-24 src/seq2seq/main.py
Update model_args

@@ -18,14 +18,14 @@ model_args = {
     "overwrite_output_dir": True,
     "max_seq_length": 256,
     "train_batch_size": 8,
-    "num_train_epochs": 32,
+    "num_train_epochs": 128,
     "max_length": 256,
-    "learning_rate": 1e-4,
+    "learning_rate": 3e-5,
     "save_eval_checkpoints": False,
-    "save_model_every_epoch": True,
+    "save_model_every_epoch": False,
     "save_best_model": False,
     "save_steps": 100000,
-    "num_beams": 5,
+    "num_beams": 3,
     "gradient_accumulation_steps": 1,
     "use_multiprocessing": False,
 }

### 2020-06-24 paper/paper.tex
Load model based on saved args
Update paper

@@
 \documentclass[letterpaper]{article}
+
 \usepackage{aaai}
@@
 \usepackage{hyperref}
+\usepackage{siunitx}
+\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
 
@@
     /Title (Sequence-to-sequence Architecture Using BERT)
-    /Author (Claudio Scheer, José Fernando Possebon)
+    /Author (Claudio Scheer, Jos\'e Fernando Possebon)
 }
@@
 \title{Sequence-to-sequence Architecture\\Using BERT}
-\author{Claudio Scheer \and José Fernando Possebon\\
+\author{Claudio Scheer \and Jos\'e Fernando Possebon\\
     Pontifical Catholic University of Rio Grande do Sul - PUCRS\\
@@
 
-In this section, we will discuss the sequence-to-sequence model using recurrent neural networks and transformers. Also, in a nutshell, we discuss how a BERT model works.
+In this section, we will discuss the sequence-to-sequence model using recurrent neural networks and transformers. In addition, we also discuss how a BERT model works.
 
@@
 The dataset contains only the raw data of the emails.
-Therefore, we created a parser\footnote{\href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{https://www.kaggle.com/claudioscheer/extract-reply-emails}} to extract the email and the replies from each email.
+Therefore, we created a parser\footnote{\href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{https://www.kaggle.com/claudioscheer/extract-reply-emails}} to extract the email and the replies from the raw data of the email.
 
@@
 
-The original dataset contains 517,401 raw emails. After parsing the raw dataset, we created a dataset with 110,205 input and target pairs.
+The original dataset contains \num{517401} raw emails.
+After parsing the raw dataset, we created a dataset with \num{110205} input and target pairs.
+As we have limited resources available, we limit the length of emails to \num{256} characters.
+We ended up with \num{40062} emails with reply in the dataset.
 
-In the parsed dataset, we have 8,368 pairs with specifics email and reply patterns. Since these pairs do not represent a large part of the dataset, we trained the dataset with this "wrong" data.
+Of that total, we selected \num{10002} emails to train the sequence-to-sequence model. From the rest of the emails, we chose random emails to evaluate the model, as shown in Section~Results.
+
+\section{Implementation}
+
+We use a pre-trained BERT model, provided by Hugging Face\footnote{\href{https://huggingface.co/}{https://huggingface.co/}}.
+Hugging Face also provides a PyTorch library for using the pre-trained models.
+Therefore, this library was used to implement the sequence-to-sequence model.
+
+To train the model, we use the following hyperparameters:
+
+\begin{itemize}
+    \item Learning rate: \num{3e-5};
+    \item Epochs: \num{128};
+    \item Adam epsilon: \num{1e-08};
+    \item Batch size: \num{8};
+    \item Beam search hypothesis: \num{3};
+\end{itemize}
+
+The batch size was limited by the amount of memory available on the GPU used to train the model. A TITAN X with 12 GB of memory was used. \num{8} was the highest possible number.
+
+Different values were tested for the learning rate and epochs.
+We did not change the default value for Adam epsilon.
+We also tested to accumulate gradients from more than one batch, but did not get good results.
+
+Training the sequence-to-sequence model in less epochs resulted in a model with a lot of noise in the reply email.
+As we had a limited batch size, increasing epochs increased the training time considerably.
+Training time is also the reason why the entire dataset was not used.
+The final model took about \num{6} days to train.
+
+When we increased the learning rate to \num{1e-4}, the model converged faster until the value of the loss function was about \num{2}\footnote{We forgot to capture the loss values over the training epochs.
+And, as the GPU is shared with other research groups, and we had monopolized the GPU for about three weeks, we were unable to run the experiments again.}.
+After that point, the loss started to increase and decrease according to the batch.
+This same behavior is true when using \num{3e-5} as learning rate.
+However, the difference is that the loss function starts to have this behavior when the loss value is closer to zero.
+
+The last changed hyperparameter was the number of hypothesis explored in each branch of the beam search.
+We tested a number greater than \num{3}.
+However, higher values resulted in some words being out of context in the generated reply email.
+
+\section{Results}
+
+https://huggingface.co/blog/how-to-generate
 

### 2020-06-25 src/seq2seq/lib/global_args.py
Log loss and learning rate

@@ -43,7 +43,6 @@ global_args = {
     "save_steps": 2000,
     "save_optimizer_and_scheduler": True,
     "silent": False,
-    "tensorboard_dir": None,
     "train_batch_size": 8,
     "use_cached_eval_features": False,
     "use_early_stopping": False,

### 2020-06-25 src/seq2seq/lib/seq2seq_model.py

@@ -6,6 +6,7 @@ import random
 import warnings
 from multiprocessing import cpu_count
 from pathlib import Path
+import csv
 
 import numpy as np
 from tqdm.auto import tqdm, trange
@@ -14,7 +15,6 @@ import pandas as pd
 import torch
 from .global_args import global_args
 from .seq2seq_utils import Seq2SeqDataset, SimpleSummarizationDataset
-from tensorboardX import SummaryWriter
 from torch.nn.utils.rnn import pad_sequence
 from torch.utils.data import DataLoader, Dataset, RandomSampler, SequentialSampler
 from torch.utils.data.distributed import DistributedSampler
@@ -277,7 +277,10 @@ class Seq2SeqModel:
         model = self.model
         args = self.args
 
-        tb_writer = SummaryWriter(logdir=args["tensorboard_dir"])
+        csv_file = open("outputs/log.csv", "w")
+        csv_file_writer = csv.writer(csv_file, delimiter=",", quotechar='"', quoting=csv.QUOTE_ALL)
+        csv_file_writer.writerow(["step", "lr", "loss"])
+
         train_sampler = RandomSampler(train_dataset)
         train_dataloader = DataLoader(train_dataset, sampler=train_sampler, batch_size=args["train_batch_size"])
 
@@ -408,8 +411,7 @@ class Seq2SeqModel:
 
                     if args["logging_steps"] > 0 and global_step % args["logging_steps"] == 0:
                         # Log metrics
-                        tb_writer.add_scalar("lr", scheduler.get_lr()[0], global_step)
-                        tb_writer.add_scalar("loss", (tr_loss - logging_loss) / args["logging_steps"], global_step)
+                        csv_file_writer.writerow([global_step, scheduler.get_lr()[0], (tr_loss - logging_loss) / args["logging_steps"]])
                         logging_loss = tr_loss
                         if args["wandb_project"]:
                             wandb.log(
@@ -425,8 +427,6 @@ class Seq2SeqModel:
                     if args["evaluate_during_training"] and (args["evaluate_during_training_steps"] > 0 and global_step % args["evaluate_during_training_steps"] == 0):
                         # Only evaluate when single GPU otherwise metrics may not average well
                         results = self.eval_model(eval_data, verbose=verbose and args["evaluate_during_training_verbose"], silent=args["evaluate_during_training_silent"], **kwargs,)
-                        for key, value in results.items():
-                            tb_writer.add_scalar("eval_{}".format(key), value, global_step)
 
[…]

### 2020-06-25 src/seq2seq/main.py

@@ -9,7 +9,7 @@ transformers_logger = logging.getLogger("transformers")
 transformers_logger.setLevel(logging.WARNING)
 
 file_path = os.path.dirname(os.path.abspath(__file__))
-train_df = pd.read_csv(os.path.join(file_path, "../../dataset/input-target-256-dev.csv"))
+train_df = pd.read_csv(os.path.join(file_path, "../../dataset/input-target-256.csv"))
 train_df.drop(train_df.columns[[0]], axis=1, inplace=True)
 train_df.dropna(subset=["input_text", "target_text"], inplace=True)
 
@@ -17,10 +17,11 @@ model_args = {
     "fp16": False,
     "overwrite_output_dir": True,
     "max_seq_length": 256,
+    "eval_batch_size": 1,
     "train_batch_size": 8,
-    "num_train_epochs": 128,
+    "num_train_epochs": 32,
     "max_length": 256,
-    "learning_rate": 3e-5,
+    "learning_rate": 1e-4,
     "save_eval_checkpoints": False,
     "save_model_every_epoch": False,
     "save_best_model": False,
@@ -28,6 +29,8 @@ model_args = {
     "num_beams": 3,
     "gradient_accumulation_steps": 1,
     "use_multiprocessing": False,
+    "logging_steps": 50,
+    "adam_epsilon": 1e-4,
 }
 
 model = Seq2SeqModel(encoder_type="bert", encoder_name="bert-base-cased", decoder_name="bert-base-cased", args=model_args)

### 2020-06-25 src/seq2seq/main.py
Load small dataset

@@ -9,7 +9,7 @@ transformers_logger = logging.getLogger("transformers")
 transformers_logger.setLevel(logging.WARNING)
 
 file_path = os.path.dirname(os.path.abspath(__file__))
-train_df = pd.read_csv(os.path.join(file_path, "../../dataset/input-target-256.csv"))
+train_df = pd.read_csv(os.path.join(file_path, "../../dataset/input-target-256-dev-small.csv"))
 train_df.drop(train_df.columns[[0]], axis=1, inplace=True)
 train_df.dropna(subset=["input_text", "target_text"], inplace=True)
 

### 2020-06-25 paper/paper.tex
Load small dataset
Update paper

@@
     Pontifical Catholic University of Rio Grande do Sul - PUCRS\\
-    claudio.scheer@edu.pucrs.br,
-    jose.possebon@edu.pucrs.br
+    \{claudio.scheer, jose.possebon\}@edu.pucrs.br
 }
@@
 
-\cite{DBLP:journals/corr/BahdanauCB14} - Proposed attention
-
-\cite{DBLP:journals/corr/VaswaniSPUJGKP17} - Attention is all you need
+ - Attention is all you need
 
@@
 
-\cite{DBLP:journals/corr/abs-1810-04805} - BERT
+BERT is a short for Bidirectional Encoder Representations from Transformers, proposed by \cite{DBLP:journals/corr/abs-1810-04805}.
+Transformers network was proposed by \cite{DBLP:journals/corr/VaswaniSPUJGKP17} and use the attentions mechanism, proposed by \cite{DBLP:journals/corr/BahdanauCB14}, to learn representations between words that can express their contextual meaning.
 
-Similarly to the original sequence-to-sequence model using a recurrent neural network, the model discussed in this paper uses two BERT neural network: one neural network to encode the input and another to decode the input encoded.
+The original BERT model was pre-trained in a corpus comprising Wikipedia and Book Corpus.
+BERT has two pre-trained models available: BERT large, with \num{345}{M} parameters (24 layers) and BERT base, with \num{110}{M} (12 layers).
+
+The model was pre-trained for masked language modeling nas next sentence predictions tasks.
+However, with the replacement of the last layer and fine-tuning, the model can be used for other tasks, using the same parameters as the original BERT model.
 
@@
 Therefore, this library was used to implement the sequence-to-sequence model.
+
+The \texttt{BertModel} class provided by Hugging Face can behave as an encoder or decoder.
+The difference is that, for the encoder, only a layer of self-attention is used and, for decoder, a layer of cross-attention is added between the layers of self-attention.
+In a nutshell, the difference is that self-attention is only applied to the input sequence, while cross-attention is applied to the input and output sentences.
+
+we used the bert base
 
@@
 
+The evaluation of the model was
+
 https://huggingface.co/blog/how-to-generate

### 2020-06-25 src/seq2seq/main.py

@@ -9,7 +9,7 @@ transformers_logger = logging.getLogger("transformers")
 transformers_logger.setLevel(logging.WARNING)
 
 file_path = os.path.dirname(os.path.abspath(__file__))
-train_df = pd.read_csv(os.path.join(file_path, "../../dataset/input-target-256-dev-small.csv"))
+train_df = pd.read_csv(os.path.join(file_path, "../../dataset/input-target-256-dev-small-small.csv"))
 train_df.drop(train_df.columns[[0]], axis=1, inplace=True)
 train_df.dropna(subset=["input_text", "target_text"], inplace=True)
 

### 2020-06-25 src/seq2seq/main.py
Use warmup_steps

@@ -31,6 +31,7 @@ model_args = {
     "use_multiprocessing": False,
     "logging_steps": 50,
     "adam_epsilon": 1e-4,
+    "warmup_steps": 10000,
 }
 
 model = Seq2SeqModel(encoder_type="bert", encoder_name="bert-base-cased", decoder_name="bert-base-cased", args=model_args)

### 2020-06-25 src/evaluate.py
Obtain BLEU score for generated replies

@@ -1,0 +1,53 @@
+import logging
+import sys
+from torchtext.data.metrics import bleu_score
+from transformers import BertTokenizer
+from lib import Seq2SeqModel
+
+
+logging.basicConfig(level=logging.INFO)
+transformers_logger = logging.getLogger("transformers")
+transformers_logger.setLevel(logging.WARNING)
+
+dataset = [
+    ("that is fine.", "Thank you."),
+    ("Are you coming back to work?  Or are you going home?", "i am coming back to work.   do you need me to take you to pick up your car?"),
+    ("you look so handsome today!", "you are making me blush."),
+    ("hey what does your middle initial  H stand for", "Harris"),
+    (
+        "Nella here is a list of products that we would launch on EOL in NETCO.  Assume the the products listed under the Financial heading are launched on day 1 and the the products listed under the Physical heading are launched at a later date.",
+        "JOHN, NO LIST ATTACHED.  PLEASE RESEND. THANKS, NELLA",
+    ),
+    ("i don't even know your salary now.", "175,000"),
+    (
+        """Zuf:
+
+        Howdy!  I hope all is well.
+
+        What is your fax# @ work?
+
+        Brother Smith""",
+        "403-974-6706",
+    ),
+    ("Friendly reminder.", "I'll be there"),
+]
+
+# model = Seq2SeqModel(encoder_decoder_type="bert", encoder_decoder_name="outputs")
+# outputs = model.predict([x[0] for x in dataset])
+
+outputs = [
+    "Thank you. all the best.",
+    "i am coming back to work. do you need me to take you to pick up your car?",
+    "you are making me blush.",
+    "Harris",
+    "ETS - ASAP is still active. I will let you know what the status of the EPMI and NNG pipelines. Thanks, Melba",
+    "haha. i am going to buy a car for you. why don't you call me about that?..",
+    "a secret for me too? What time are you going to be in town? I will be out of town on Friday. Chris",
+    "Thanks. of course you'll be taking some time off. too much risk.",
+]
+tokenizer = BertTokenizer.from_pretrained("bert-base-cased")
+
+candidate_corpus = [tokenizer.tokenize(x[1]) for x in dataset]
+references_corpus = [[tokenizer.tokenize(x)] for x in outputs]
+bleu = bleu_score(candidate_corpus, references_corpus)
+print(bleu)

### 2020-06-25 src/main.py

@@ -9,7 +9,7 @@ transformers_logger = logging.getLogger("transformers")
 transformers_logger.setLevel(logging.WARNING)
 
 file_path = os.path.dirname(os.path.abspath(__file__))
-train_df = pd.read_csv(os.path.join(file_path, "../../dataset/input-target-256-dev-small-small.csv"))
+train_df = pd.read_csv(os.path.join(file_path, "../dataset/input-target-256-dev-small-small.csv"))
 train_df.drop(train_df.columns[[0]], axis=1, inplace=True)
 train_df.dropna(subset=["input_text", "target_text"], inplace=True)
 

### 2020-06-25 src/seq2seq/lib/__init__.py

@@ -1,1 +1,0 @@
-from .seq2seq_model import Seq2SeqModel

### 2020-06-25 src/seq2seq/lib/global_args.py

@@ -1,58 +1,0 @@
-from multiprocessing import cpu_count
-import sys
-
-
-global_args = {
-    "adam_epsilon": 1e-8,
-    "best_model_dir": "outputs/best_model",
-    "cache_dir": "cache_dir/",
-    "config": {},
-    "do_lower_case": False,
-    "early_stopping_consider_epochs": False,
-    "early_stopping_delta": 0,
-    "early_stopping_metric": "eval_loss",
-    "early_stopping_metric_minimize": True,
-    "early_stopping_patience": 3,
-    "encoding": None,
-    "eval_batch_size": 8,
-    "evaluate_during_training": False,
-    "evaluate_during_training_silent": True,
-    "evaluate_during_training_steps": 2000,
-    "evaluate_during_training_verbose": False,
-    "fp16": True,
-    "fp16_opt_level": "O1",
-    "gradient_accumulation_steps": 1,
-    "learning_rate": 4e-5,
-    "local_rank": -1,
-    "logging_steps": 50,
-    "manual_seed": None,
-    "max_grad_norm": 1.0,
-    "max_seq_length": 128,
-    "multiprocessing_chunksize": 500,
-    "n_gpu": 1,
-    "no_cache": False,
-    "no_save": False,
-    "num_train_epochs": 1,
-    "output_dir": "outputs/",
-    "overwrite_output_dir": False,
-    "process_count": cpu_count() - 2 if cpu_count() > 2 else 1,
-    "reprocess_input_data": True,
-    "save_best_model": True,
-    "save_eval_checkpoints": True,
-    "save_model_every_epoch": True,
-    "save_steps": 2000,
-    "save_optimizer_and_scheduler": True,
-    "silent": False,
-    "train_batch_size": 8,
-    "use_cached_eval_features": False,
-    "use_early_stopping": False,
-    "use_multiprocessing": True,
-    "wandb_kwargs": {},
-    "wandb_project": None,
-    "warmup_ratio": 0.06,
-    "warmup_steps": 0,
-    "weight_decay": 0,
-}
-
-if sys.platform == "win32":
-    global_args["process_count"] = min(global_args["process_count"], 61)

### 2020-06-25 src/seq2seq/lib/seq2seq_model.py

@@ -1,854 +1,0 @@
-import json
-import logging
-import math
-import os
-import random
-import warnings
-from multiprocessing import cpu_count
-from pathlib import Path
-import csv
-
-import numpy as np
-from tqdm.auto import tqdm, trange
-
-import pandas as pd
-import torch
-from .global_args import global_args
-from .seq2seq_utils import Seq2SeqDataset, SimpleSummarizationDataset
-from torch.nn.utils.rnn import pad_sequence
-from torch.utils.data import DataLoader, Dataset, RandomSampler, SequentialSampler
-from torch.utils.data.distributed import DistributedSampler
-from transformers import AdamW, EncoderDecoderModel, EncoderDecoderConfig, get_linear_schedule_with_warmup
-from transformers import (
-    AutoModel,
-    AutoTokenizer,
-    AutoConfig,
-    BertTokenizer,
-    BertModel,
-    BertForMaskedLM,
-    BertConfig,
-    CamembertConfig,
-    CamembertModel,
-    CamembertTokenizer,
-    DistilBertConfig,
-    DistilBertModel,
-    DistilBertTokenizer,
-    ElectraConfig,
-    ElectraModel,
-    ElectraTokenizer,
-    LongformerConfig,
-    LongformerModel,
-    LongformerTokenizer,
-    PreTrainedModel,
-    PreTrainedTokenizer,
-    RobertaConfig,
-    RobertaModel,
-    RobertaTokenizer,
-    BartForConditionalGeneration,
-    BartTokenizer,
-    BartConfig,
-    MarianMTModel,
-    MarianTokenizer,
-    MarianConfig,
-)
-
-try:
-    import wandb
-
-    wandb_available = True
-except ImportError:
-    wandb_available = False
-
-logger = logging.getLogger(__name__)
-
-MODEL_CLASSES = {
-    "auto": (AutoConfig, AutoModel, AutoTokenizer),
-    "bart": (BartConfig, BartForConditionalGeneration, BartTokenizer),
-    "bert": (BertConfig, BertModel, BertTokenizer),
-    "camembert": (CamembertConfig, CamembertModel, CamembertTokenizer),
-    "distilbert": (DistilBertConfig, DistilBertModel, DistilBertTokenizer),
-    "electra": (ElectraConfig, ElectraModel, ElectraTokenizer),
-    "longformer": (LongformerConfig, LongformerModel, LongformerTokenizer),
[…]

### 2020-06-25 src/seq2seq/lib/seq2seq_utils.py

@@ -1,97 +1,0 @@
-import logging
-import os
-import pickle
-from multiprocessing import Pool
-from typing import Tuple
-
-from tqdm.auto import tqdm
-
-import pandas as pd
-import torch
-from tokenizers.implementations import ByteLevelBPETokenizer
-from tokenizers.processors import BertProcessing
-from torch.utils.data import Dataset
-from transformers import PreTrainedTokenizer
-
-logger = logging.getLogger(__name__)
-
-
-def preprocess_data(data):
-    input_text, target_text, encoder_tokenizer, decoder_tokenizer, args = data
-
-    input_text = encoder_tokenizer.encode(input_text, max_length=args["max_seq_length"], pad_to_max_length=True, return_tensors="pt",)
-
-    target_text = decoder_tokenizer.encode(target_text, max_length=args["max_seq_length"], pad_to_max_length=True, return_tensors="pt")
-    return (torch.flatten(input_text), torch.flatten(target_text))
-
-
-class Seq2SeqDataset(Dataset):
-    def __init__(self, encoder_tokenizer, decoder_tokenizer, args, data, mode):
-        cached_features_file = os.path.join(args["cache_dir"], args["model_name"] + "_cached_" + str(args["max_seq_length"]) + str(len(data)))
-
-        if os.path.exists(cached_features_file) and ((not args["reprocess_input_data"] and not args["no_cache"]) or (mode == "dev" and args["use_cached_eval_features"] and not args["no_cache"])):
-            logger.info(" Loading features from cached file %s", cached_features_file)
-            with open(cached_features_file, "rb") as handle:
-                self.examples = pickle.load(handle)
-        else:
-            logger.info(" Creating features from dataset file at %s", args["cache_dir"])
-
-        data = [(input_text, target_text, encoder_tokenizer, decoder_tokenizer, args) for input_text, target_text in zip(data["input_text"], data["target_text"])]
-
-        if args["use_multiprocessing"]:
-            with Pool(args["process_count"]) as p:
-                self.examples = list(tqdm(p.imap(preprocess_data, data, chunksize=args["multiprocessing_chunksize"]), total=len(data), disable=args["silent"],))
-        else:
-            self.examples = [preprocess_data(d) for d in tqdm(data, disable=args["silent"])]
-
-        logger.info(" Saving features into cached file %s", cached_features_file)
-        with open(cached_features_file, "wb") as handle:
[…]

### 2020-06-25 slides/slides.tex
Update paper and slides

@@
 \documentclass{beamer}
+
+\usepackage{lmodern}
 \usepackage[utf8]{inputenc}
-
-\usepackage{utopia} %font utopia imported
+\usepackage{utopia}
+\usepackage{hyperref}
+\usepackage{tabularx}
+\usepackage{siunitx}
+\sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
 
@@
 %------------------------------------------------------------
-%This block of code defines the information to appear in the
-%Title page
-\title[About Beamer] %optional
+\title[About Beamer]
 {About the Beamer class in presentation making}
@@
 
-\author[Arthur, Doe] % (optional)
-{A.~B.~Arthur\inst{1} \and J.~Doe\inst{2}}
+\author[Claudio, Jos\'e]
+{Claudio Scheer\inst{1} \and Jos\'e Fernando Possebon\inst{1}}
 
-\institute[VFU] % (optional)
+\institute[PUCRS]
 {
   \inst{1}%
-  Faculty of Physics\\
-  Very Famous University
-  \and
-  \inst{2}%
-  Faculty of Chemistry\\
-  Very Famous University
+  Pontifical Catholic University of Rio Grande do Sul - PUCRS\\
+  \{claudio.scheer, jose.possebon\}@edu.pucrs.br
 }
 
-\date[VLC 2014] % (optional)
-{Very Large Conference, April 2014}
-
-%End of title page configuration block
-%------------------------------------------------------------
-
-%------------------------------------------------------------
-%The next block of commands puts the table of contents at the 
-%beginning of each section and highlights the current section:
+\date[Deep Learning 2020]
+{Deep Learning, June 2020}
 
@@
 
-%The next statement creates the title page.
 \frame{\titlepage}
@@
 %---------------------------------------------------------
-%This block of code is for the table of contents after
-%the title page
 \begin{frame}
@@
 
-\section{First section}
+%---------------------------------------------------------
+\section{Proposal}
 
-%---------------------------------------------------------
-%Changing visivility of the text
 \begin{frame}
-\frametitle{Sample frame title}
-This is a text in second frame. For the sake of showing an example.
+  \frametitle{Proposal}
 
-\begin{itemize}
-    \item<1-> Text visible on slide 1
-    \item<2-> Text visible on slide 2
-    \item<3> Text visible on slides 3
-    \item<4-> Text visible on slide 4
-\end{itemize}
+  % \begin{itemize}
+  %   \item<1-> Text visible on slide 1
+  %   \item<2-> Text visible on slide 2
+  %   \item<3> Text visible on slides 3
+  %   \item<4-> Text visible on slide 4
+  % \end{itemize}
 \end{frame}
 
+% \begin{frame}
+%   In this slide \pause
+
+%   the text will be partially visible \pause
+
+%   And finally everything will be there
+% \end{frame}
 %---------------------------------------------------------
@@
 %---------------------------------------------------------
-%Example of the \pause command
+\section{Dataset}
+
 \begin{frame}
-In this slide \pause
+  \frametitle{The Enron Email Dataset}
 
-the text will be partially visible \pause
+  {\scriptsize
+    no, i dont mind.       : - )
+    \bigbreak
+    -----Original Message-----
+    \bigbreak
+    Hi how are you doing?  I have a meeting from 4 to 5, do you mind waiting for me?  Thanks.
 
-And finally everything will be there
+    John
+    \bigbreak
+    -----Original Message-----
+    \bigbreak
+    hello
+  }
 \end{frame}
-%---------------------------------------------------------
 
-\section{Second section}
+\begin{frame}
+  \frametitle{The Enron Email Dataset}
 
-%---------------------------------------------------------
-%Highlighting text
+  \begin{itemize}
+    \item \href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{https://www.kaggle.com/claudioscheer/extract-reply-emails};
+    \item Get only emails with less than 256 characters;
+  \end{itemize}
+
+  \bigbreak
+  \bigbreak
+  \bigbreak
+
+  Final dataset: \num{40062} input-target pairs.
+  \\
+  Train dataset: \num{10002} input-target pairs.
+\end{frame}
+
 \begin{frame}
-\frametitle{Sample frame title}
+  \frametitle{Samples}
 
-In this slide, some important text will be
-\alert{highlighted} because it's important.
-Please, don't abuse it.
-
-\begin{block}{Remark}
-Sample text
-\end{block}
-
-\begin{alertblock}{Important theorem}
-Sample text in red box
-\end{alertblock}
-
-\begin{examples}
-Sample text in green box. The title of the block is ``Examples".
-\end{examples}
+  \begin{table}
+    \centering
+    \begin{tabularx}{\textwidth}{|X|X|}
+      \hline
+      \textbf{Input}                                                            & \textbf{Target}                                                                       \\
+      \hline
+      I thought this one was canceled. So I declined to get it off my calendar. & You're right.                                                                         \\
+      \hline
+      Rex - thanks for the quick response...please note the revised letters below.
+      Previous email had a clerical error                                       & Who will sign theses?                                                                 \\
+      \hline
+      Where can I get info on safety statistics for the pipes?                  & Ralph, please get with Rod and provide what ever he needs in the way of Safety Stats. \\
+      \hline
+    \end{tabularx}
+  \end{table}
 \end{frame}
@@
 %---------------------------------------------------------
-%Two columns
+\section{BERT}
+
 \begin{frame}
-\frametitle{Two-column slide}
+  \frametitle{BERT architecture}
+\end{frame}
 
-\begin{columns}
+\begin{frame}
+  \frametitle{Hugging Face}
 
-\column{0.5\textwidth}
-This is a text in first column.
-$$E=mc^2$$
   \begin{itemize}
-\item First item
-\item Second item
+    \item BERT base was used;
+          \begin{itemize}
+            \item 12 layers;
+          \end{itemize}
+    \item Hugging Face and PyTorch was used;
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Learning Rate Schedule}
+
+  \begin{itemize}
+    \item Warm-up steps: \num{10000};
+    \item Learning rate: \num{1e-4};
   \end{itemize}
 
-\column{0.5\textwidth}
-This text will be in the second column
-and on a second tought this is a nice looking
-layout in some cases.
-\end{columns}
+  \bigbreak
+  \bigbreak
+
+  \includegraphics[width=\textwidth]{../latex-data/images/warmup_linear_schedule.png}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Optimizer and hyperparameters}
+
+  \begin{itemize}
+    \item Adam;
+          \begin{itemize}
+            \item Adam epsilon: \num{1e-4};
+          \end{itemize}
+    \item Batch size: \num{8};
+    \item Training epochs: \num{32};
+    \item Beam search hypothesis: \num{3};
+  \end{itemize}
+\end{frame}
+%---------------------------------------------------------
+
+%---------------------------------------------------------
+\section{Results}
+
+\begin{frame}
+  \frametitle{Generated replies}
+
+  \begin{table}
+    \centering
+    \begin{tabularx}{\textwidth}{|X|X|c|}
+      \hline
+      \textbf{Email}                      & \textbf{Reply}                                                                              & \textbf{AI?} \\
+      \hline
+      Shall we have the meeting tomorrow? & meeting is postponed because the 3 : 00 p. m. meeting today. meeting is canceled for today. & \num{30}{\%} \\
+      \hline
+      hi                                  & Hi how are you?                                                                             & \num{10}{\%} \\
+      \hline
+      you look so handsome today          & why thank you, you do as well                                                               & \num{30}{\%} \\
+      \hline
+    \end{tabularx}
+  \end{table}
 \end{frame}

### 2020-06-25 src/main.py
Change number of epochs

@@ -19,13 +19,13 @@ model_args = {
     "max_seq_length": 256,
     "eval_batch_size": 1,
     "train_batch_size": 8,
-    "num_train_epochs": 32,
+    "num_train_epochs": 8,
     "max_length": 256,
     "learning_rate": 1e-4,
     "save_eval_checkpoints": False,
     "save_model_every_epoch": False,
     "save_best_model": False,
-    "save_steps": 100000,
+    "save_steps": 20000,
     "num_beams": 3,
     "gradient_accumulation_steps": 1,
     "use_multiprocessing": False,

### 2020-06-25 src/main.py
Change warmup_steps

@@ -31,7 +31,7 @@ model_args = {
     "use_multiprocessing": False,
     "logging_steps": 50,
     "adam_epsilon": 1e-4,
-    "warmup_steps": 10000,
+    "warmup_steps": 5000,
 }
 
 model = Seq2SeqModel(encoder_type="bert", encoder_name="bert-base-cased", decoder_name="bert-base-cased", args=model_args)

### 2020-06-25 src/main.py
Save model every epoch

@@ -23,7 +23,7 @@ model_args = {
     "max_length": 256,
     "learning_rate": 1e-4,
     "save_eval_checkpoints": False,
-    "save_model_every_epoch": False,
+    "save_model_every_epoch": True,
     "save_best_model": False,
     "save_steps": 20000,
     "num_beams": 3,

### 2020-06-25 src/main.py
Update number of epochs

@@ -19,11 +19,11 @@ model_args = {
     "max_seq_length": 256,
     "eval_batch_size": 1,
     "train_batch_size": 8,
-    "num_train_epochs": 8,
+    "num_train_epochs": 16,
     "max_length": 256,
     "learning_rate": 1e-4,
     "save_eval_checkpoints": False,
-    "save_model_every_epoch": True,
+    "save_model_every_epoch": False,
     "save_best_model": False,
     "save_steps": 20000,
     "num_beams": 3,

### 2020-06-25 src/main.py
Update args

@@ -9,7 +9,7 @@ transformers_logger = logging.getLogger("transformers")
 transformers_logger.setLevel(logging.WARNING)
 
 file_path = os.path.dirname(os.path.abspath(__file__))
-train_df = pd.read_csv(os.path.join(file_path, "../dataset/input-target-256-dev-small-small.csv"))
+train_df = pd.read_csv(os.path.join(file_path, "../dataset/input-target-256.csv"))
 train_df.drop(train_df.columns[[0]], axis=1, inplace=True)
 train_df.dropna(subset=["input_text", "target_text"], inplace=True)
 
@@ -18,7 +18,7 @@ model_args = {
     "overwrite_output_dir": True,
     "max_seq_length": 256,
     "eval_batch_size": 1,
-    "train_batch_size": 8,
+    "train_batch_size": 12,
     "num_train_epochs": 16,
     "max_length": 256,
     "learning_rate": 1e-4,

### 2020-06-25 src/lib/global_args.py
Add lib

@@ -1,0 +1,58 @@
+from multiprocessing import cpu_count
+import sys
+
+
+global_args = {
+    "adam_epsilon": 1e-8,
+    "best_model_dir": "outputs/best_model",
+    "cache_dir": "cache_dir/",
+    "config": {},
+    "do_lower_case": False,
+    "early_stopping_consider_epochs": False,
+    "early_stopping_delta": 0,
+    "early_stopping_metric": "eval_loss",
+    "early_stopping_metric_minimize": True,
+    "early_stopping_patience": 3,
+    "encoding": None,
+    "eval_batch_size": 8,
+    "evaluate_during_training": False,
+    "evaluate_during_training_silent": True,
+    "evaluate_during_training_steps": 2000,
+    "evaluate_during_training_verbose": False,
+    "fp16": True,
+    "fp16_opt_level": "O1",
+    "gradient_accumulation_steps": 1,
+    "learning_rate": 4e-5,
+    "local_rank": -1,
+    "logging_steps": 50,
+    "manual_seed": None,
+    "max_grad_norm": 1.0,
+    "max_seq_length": 128,
+    "multiprocessing_chunksize": 500,
+    "n_gpu": 1,
+    "no_cache": False,
+    "no_save": False,
+    "num_train_epochs": 1,
+    "output_dir": "outputs/",
+    "overwrite_output_dir": False,
+    "process_count": cpu_count() - 2 if cpu_count() > 2 else 1,
+    "reprocess_input_data": True,
+    "save_best_model": True,
+    "save_eval_checkpoints": True,
+    "save_model_every_epoch": True,
+    "save_steps": 2000,
+    "save_optimizer_and_scheduler": True,
+    "silent": False,
+    "train_batch_size": 8,
+    "use_cached_eval_features": False,
+    "use_early_stopping": False,
+    "use_multiprocessing": True,
+    "wandb_kwargs": {},
+    "wandb_project": None,
+    "warmup_ratio": 0.06,
+    "warmup_steps": 0,
+    "weight_decay": 0,
+}
+
+if sys.platform == "win32":
+    global_args["process_count"] = min(global_args["process_count"], 61)

### 2020-06-25 src/lib/seq2seq_model.py

@@ -1,0 +1,854 @@
+import json
+import logging
+import math
+import os
+import random
+import warnings
+from multiprocessing import cpu_count
+from pathlib import Path
+import csv
+
+import numpy as np
+from tqdm.auto import tqdm, trange
+
+import pandas as pd
+import torch
+from .global_args import global_args
+from .seq2seq_utils import Seq2SeqDataset, SimpleSummarizationDataset
+from torch.nn.utils.rnn import pad_sequence
+from torch.utils.data import DataLoader, Dataset, RandomSampler, SequentialSampler
+from torch.utils.data.distributed import DistributedSampler
+from transformers import AdamW, EncoderDecoderModel, EncoderDecoderConfig, get_linear_schedule_with_warmup
+from transformers import (
+    AutoModel,
+    AutoTokenizer,
+    AutoConfig,
+    BertTokenizer,
+    BertModel,
+    BertForMaskedLM,
+    BertConfig,
+    CamembertConfig,
+    CamembertModel,
+    CamembertTokenizer,
+    DistilBertConfig,
+    DistilBertModel,
+    DistilBertTokenizer,
+    ElectraConfig,
+    ElectraModel,
+    ElectraTokenizer,
+    LongformerConfig,
+    LongformerModel,
+    LongformerTokenizer,
+    PreTrainedModel,
+    PreTrainedTokenizer,
+    RobertaConfig,
+    RobertaModel,
+    RobertaTokenizer,
+    BartForConditionalGeneration,
+    BartTokenizer,
+    BartConfig,
+    MarianMTModel,
+    MarianTokenizer,
+    MarianConfig,
+)
+
+try:
+    import wandb
+
+    wandb_available = True
+except ImportError:
+    wandb_available = False
+
+logger = logging.getLogger(__name__)
+
+MODEL_CLASSES = {
+    "auto": (AutoConfig, AutoModel, AutoTokenizer),
+    "bart": (BartConfig, BartForConditionalGeneration, BartTokenizer),
+    "bert": (BertConfig, BertModel, BertTokenizer),
+    "camembert": (CamembertConfig, CamembertModel, CamembertTokenizer),
+    "distilbert": (DistilBertConfig, DistilBertModel, DistilBertTokenizer),
+    "electra": (ElectraConfig, ElectraModel, ElectraTokenizer),
+    "longformer": (LongformerConfig, LongformerModel, LongformerTokenizer),
[…]

### 2020-06-25 src/lib/seq2seq_utils.py

@@ -1,0 +1,97 @@
+import logging
+import os
+import pickle
+from multiprocessing import Pool
+from typing import Tuple
+
+from tqdm.auto import tqdm
+
+import pandas as pd
+import torch
+from tokenizers.implementations import ByteLevelBPETokenizer
+from tokenizers.processors import BertProcessing
+from torch.utils.data import Dataset
+from transformers import PreTrainedTokenizer
+
+logger = logging.getLogger(__name__)
+
+
+def preprocess_data(data):
+    input_text, target_text, encoder_tokenizer, decoder_tokenizer, args = data
+
+    input_text = encoder_tokenizer.encode(input_text, max_length=args["max_seq_length"], pad_to_max_length=True, return_tensors="pt",)
+
+    target_text = decoder_tokenizer.encode(target_text, max_length=args["max_seq_length"], pad_to_max_length=True, return_tensors="pt")
+    return (torch.flatten(input_text), torch.flatten(target_text))
+
+
+class Seq2SeqDataset(Dataset):
+    def __init__(self, encoder_tokenizer, decoder_tokenizer, args, data, mode):
+        cached_features_file = os.path.join(args["cache_dir"], args["model_name"] + "_cached_" + str(args["max_seq_length"]) + str(len(data)))
+
+        if os.path.exists(cached_features_file) and ((not args["reprocess_input_data"] and not args["no_cache"]) or (mode == "dev" and args["use_cached_eval_features"] and not args["no_cache"])):
+            logger.info(" Loading features from cached file %s", cached_features_file)
+            with open(cached_features_file, "rb") as handle:
+                self.examples = pickle.load(handle)
+        else:
+            logger.info(" Creating features from dataset file at %s", args["cache_dir"])
+
+        data = [(input_text, target_text, encoder_tokenizer, decoder_tokenizer, args) for input_text, target_text in zip(data["input_text"], data["target_text"])]
+
+        if args["use_multiprocessing"]:
+            with Pool(args["process_count"]) as p:
+                self.examples = list(tqdm(p.imap(preprocess_data, data, chunksize=args["multiprocessing_chunksize"]), total=len(data), disable=args["silent"],))
+        else:
+            self.examples = [preprocess_data(d) for d in tqdm(data, disable=args["silent"])]
+
+        logger.info(" Saving features into cached file %s", cached_features_file)
+        with open(cached_features_file, "wb") as handle:
[…]

### 2020-06-25 src/main.py
Update train_batch_size

@@ -18,7 +18,7 @@ model_args = {
     "overwrite_output_dir": True,
     "max_seq_length": 256,
     "eval_batch_size": 1,
-    "train_batch_size": 12,
+    "train_batch_size": 10,
     "num_train_epochs": 16,
     "max_length": 256,
     "learning_rate": 1e-4,

### 2020-06-26 src/plot.py
Plot loss and learning rate

@@ -1,0 +1,13 @@
+import os
+import pandas as pd
+import matplotlib.pyplot as plt
+
+
+file_path = os.path.dirname(os.path.abspath(__file__))
+csv = pd.read_csv(os.path.join(file_path, "../outputs/log.csv"))
+
+csv["loss"].plot.line()
+
+plt.xlabel("Steps")
+plt.ylabel("Loss")
+plt.show()

### 2020-06-26 latex/paper/paper.tex
Rearrange the paper and slides folders
Update paper

--- 2020-06-25 paper/paper.tex
@@
 \usepackage{siunitx}
+\usepackage{graphicx}
 \sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
@@
 
+discuss it here
+
+In a nutshell, the difference is that self-attention is only applied to the input sequence, while cross-attention is applied to the input and output sentences.
+
 \section{Dataset}
 
-As we focused our project on automatic email reply, we used The Enron Email Dataset\footnote{\href{https://www.kaggle.com/wcukierski/enron-email-dataset}{https://www.kaggle.com/wcukierski/enron-email-dataset}} to train our model.
-The dataset contains only the raw data of the emails.
-Therefore, we created a parser\footnote{\href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{https://www.kaggle.com/claudioscheer/extract-reply-emails}} to extract the email and the replies from the raw data of the email.
+As the project focus is on automatic email reply, The Enron Email Dataset\footnote{\href{https://www.kaggle.com/wcukierski/enron-email-dataset}{https://www.kaggle.com/wcukierski/enron-email-dataset}} was used to train the model.
+The dataset contains only the emails raw data.
+Therefore, a parser\footnote{\href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{https://www.kaggle.com/claudioscheer/extract-reply-emails}} was built to extract the email and the replies from the raw data of the email.
 
 To identify whether an email has a reply or not, we look for emails that contain the string \texttt{-----Original Message-----}.
-After filtering only emails with non-empty replies, we parse those emails in an input sequence (the original email) and in the target sequence (the reply email).
-The entire extraction was done automatically, that is, we did not manually extract or adjust any email.
+After filtering only emails with non-empty replies, those emails were parsed into an input sequence (the original email) and a target sequence (the reply email).
+The entire extraction was done automatically, that is, we did not extract or adjust any email manually.
 
-We used two libraries to parse the dataset: \texttt{talon}\footnote{\href{https://github.com/mailgun/talon}{https://github.com/mailgun/talon}}, provided by Mailgun, and \texttt{email}, provided by Python.
+Two libraries were used to parse the dataset: \texttt{talon}\footnote{\href{https://github.com/mailgun/talon}{https://github.com/mailgun/talon}}, provided by Mailgun, and \texttt{email}, provided by Python.
 The \texttt{email} package returns the email body with the entire thread.
-To extract only the last reply from an email thread, we use the \texttt{talon} package.
+To extract only the last reply from an email thread, the \texttt{talon} package was used.
 
 The original dataset contains \num{517401} raw emails.
-After parsing the raw dataset, we created a dataset with \num{110205} input and target pairs.
-As we have limited resources available, we limit the length of emails to \num{256} characters.
-We ended up with \num{40062} emails with reply in the dataset.
-
-Of that total, we selected \num{10002} emails to train the sequence-to-sequence model. From the rest of the emails, we chose random emails to evaluate the model, as shown in Section~Results.
+After parsing the raw dataset, the new dataset consisted of \num{110205} input and target pairs.
+As the resources available to fine-tune the model were limited,  only emails with less than \num{256} characters were used.
+The final dataset consisted of \num{40062} emails.
+All of these input and target pairs were used to train the BERT model.
 
@@
 
-We use a pre-trained BERT model, provided by Hugging Face\footnote{\href{https://huggingface.co/}{https://huggingface.co/}}.
+A pre-trained BERT model, provided by Hugging Face\footnote{\href{https://huggingface.co/}{https://huggingface.co/}}, was used.
 Hugging Face also provides a PyTorch library for using the pre-trained models.
-Therefore, this library was used to implement the sequence-to-sequence model.
+Therefore, this library was used to implement the sequence-to-sequence model, with PyTorch 1.5.1.
 
@@
 The difference is that, for the encoder, only a layer of self-attention is used and, for decoder, a layer of cross-attention is added between the layers of self-attention.
-In a nutshell, the difference is that self-attention is only applied to the input sequence, while cross-attention is applied to the input and output sentences.
+The difference between these attention mechanisms is discussed in Section~BERT.
 
-we used the bert base
-
-To train the model, we use the following hyperparameters:
+In this paper, the BERT base architecture was used. This model uses fewer resources, which allowed us to increase the batch size. To fine-tune the model, the following hyperparameters was used:
 
 \begin{itemize}
-    \item Learning rate: \num{3e-5};
-    \item Epochs: \num{128};
-    \item Adam epsilon: \num{1e-08};
-    \item Batch size: \num{8};
+    \item Learning rate: \num{1e-4};
+    \item Warm-up steps: \num{5000};
+    \item Epochs: \num{10.5};
+    \item Adam epsilon: \num{1e-4}, same as in the original BERT paper \cite{DBLP:journals/corr/abs-1810-04805};
+    \item Batch size: \num{10};
     \item Beam search hypothesis: \num{3};
@@
 
-The batch size was limited by the amount of memory available on the GPU used to train the model. A TITAN X with 12 GB of memory was used. \num{8} was the highest possible number.
+In the fine-tune process, an EC2 spot instance on AWS was used.
+A checkpoint of the model was saved every \num{20000} steps, mitigating the loss of processment if the instance was suddenly stopped.
+The instance was equipped with a 16 GB NVIDIA T4 GPU (CUDA 10.2).
 
-Different values were tested for the learning rate and epochs.
-We did not change the default value for Adam epsilon.
-We also tested to accumulate gradients from more than one batch, but did not get good results.
+The batch size was limited by the amount of GPU memory available. We also tested to accumulate and update the gradients after \num{4} steps, but we did not see any improvements.
 
-Training the sequence-to-sequence model in less epochs resulted in a model with a lot of noise in the reply email.
-As we had a limited batch size, increasing epochs increased the training time considerably.
-Training time is also the reason why the entire dataset was not used.
-The final model took about \num{6} days to train.
+Different values were tested for the learning rate and epochs, with and without warm-up.
+Figure~\ref{fig:learning-rate-schedule} shows the final results of the learning rate update during the fine-tuning process.
 
-When we increased the learning rate to \num{1e-4}, the model converged faster until the value of the loss function was about \num{2}\footnote{We forgot to capture the loss values over the training epochs.
-And, as the GPU is shared with other research groups, and we had monopolized the GPU for about three weeks, we were unable to run the experiments again.}.
-After that point, the loss started to increase and decrease according to the batch.
-This same behavior is true when using \num{3e-5} as learning rate.
-However, the difference is that the loss function starts to have this behavior when the loss value is closer to zero.
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.47\textwidth]{../images/warmup_linear_schedule.pdf}
+    \caption{Learning rate schedule}
+    \label{fig:learning-rate-schedule}
+\end{figure}
+
+Figure~\ref{fig:loss} shows the loss function value over the fine-tuning process. We do not know why, but loss function shows a greater decrease at the end of each epoch.
+
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.47\textwidth]{../images/loss_function.pdf}
+    \caption{Loss function}
+    \label{fig:loss}
+\end{figure}
+
+Some hyperparameters configuration shows bad results in the loss function. For example:
+
+\begin{itemize}
+    \item learning rates greater than \num{1e-4} did not make the model converge;
+    \item the use of a warm-up period allowed the model to converge in less epochs;
+    \item a high number of epochs almost causes an overfitting of the model;
+\end{itemize}
 
 The last changed hyperparameter was the number of hypothesis explored in each branch of the beam search.
-We tested a number greater than \num{3}.
-However, higher values resulted in some words being out of context in the generated reply email.
+A number greater than \num{3} resulted in more words being out of context in the generated reply email.
 

### 2020-06-27 src/evaluate.py
Evaluate model using evaluation dataset

@@ -1,50 +1,18 @@
-import logging
-import sys
+import os
+import pandas as pd
 from torchtext.data.metrics import bleu_score
 from transformers import BertTokenizer
-from lib import Seq2SeqModel
 
 
-logging.basicConfig(level=logging.INFO)
-transformers_logger = logging.getLogger("transformers")
-transformers_logger.setLevel(logging.WARNING)
+file_path = os.path.dirname(os.path.abspath(__file__))
+evaluation_df = pd.read_csv(os.path.join(file_path, "../dataset/input-target-256-evaluation.csv"))
 
-dataset = [
-    ("that is fine.", "Thank you."),
-    ("Are you coming back to work?  Or are you going home?", "i am coming back to work.   do you need me to take you to pick up your car?"),
-    ("you look so handsome today!", "you are making me blush."),
-    ("hey what does your middle initial  H stand for", "Harris"),
-    (
-        "Nella here is a list of products that we would launch on EOL in NETCO.  Assume the the products listed under the Financial heading are launched on day 1 and the the products listed under the Physical heading are launched at a later date.",
-        "JOHN, NO LIST ATTACHED.  PLEASE RESEND. THANKS, NELLA",
-    ),
-    ("i don't even know your salary now.", "175,000"),
-    (
-        """Zuf:
+dataset = []
+outputs = []
+for i, x in evaluation_df.iterrows():
+    dataset.append((str(x["input_text"]), str(x["target_text"])))
+    outputs.append(str(x["generated_reply"]))
 
-        Howdy!  I hope all is well.
-
-        What is your fax# @ work?
-
-        Brother Smith""",
-        "403-974-6706",
-    ),
-    ("Friendly reminder.", "I'll be there"),
-]
-
-# model = Seq2SeqModel(encoder_decoder_type="bert", encoder_decoder_name="outputs")
-# outputs = model.predict([x[0] for x in dataset])
-
-outputs = [
-    "Thank you. all the best.",
-    "i am coming back to work. do you need me to take you to pick up your car?",
-    "you are making me blush.",
-    "Harris",
-    "ETS - ASAP is still active. I will let you know what the status of the EPMI and NNG pipelines. Thanks, Melba",
-    "haha. i am going to buy a car for you. why don't you call me about that?..",
-    "a secret for me too? What time are you going to be in town? I will be out of town on Friday. Chris",
[…]

### 2020-06-27 latex/paper/paper.tex
Update paper

@@
 \usepackage{hyperref}
+\usepackage{tabularx}
 \usepackage{siunitx}
 \usepackage{graphicx}
+\usepackage{todonotes}
 \sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
@@
 \pdfinfo{
-    /Title (Sequence-to-sequence Architecture Using BERT)
+    /Title (Email Autoresponder using a Sequence-to-sequence Architecture with BERT)
     /Author (Claudio Scheer, Jos\'e Fernando Possebon)
@@
 %
-\title{Sequence-to-sequence Architecture\\Using BERT}
+\title{Email Autoresponder using a Sequence-to-sequence\\Architecture with BERT}
 \author{Claudio Scheer \and Jos\'e Fernando Possebon\\
@@
     \begin{quote}
-        Abstract.
+        Due to the large number of emails that people receive, it is not just about filtering what is spam or not, but it is also essential to help people filter what requires their attention from something that can be done by an intelligent agent.
+If we consider the scenario of a sales representative who sells software licenses, for example, it is common to receive requests for quotations from their customers about the price of software licenses.
+We believe that it is possible to implement an agent that could read the emails, understand what is requested, and respond to their emails automatically.
     \end{quote}
@@
 All of these input and target pairs were used to train the BERT model.
+
+\num{21} emails that were not correctly parsed were used to evaluate the model and obtaing the BLEU score. These emails were chosen manually from the dataset.
 
@@
 
-The evaluation of the model was
+The fine-tuned model still has some noise in the replies generated.
+Therefore, only the first part of the text of the generated replies was used.
+This is valid for the BLEU score and for the subjective evaluation.
 
-https://huggingface.co/blog/how-to-generate
+The BLEU score was used to get a quantitative result of the model.
+Using the evaluation dataset, the BLEU score was \num{0.0}.
+This does not mean that the replies were bad.
+This means that the generated replies do not match to the replies originally sent.
+Table~\ref{table:example-reply-bleu} shows some examples of why the BLEU score was \num{0.0}.
+
+\begin{table}[ht]
+    \centering
+    \begin{tabularx}{0.47\textwidth}{|X|X|X|}
+        \hline
+        \textbf{Input}                                                  & \textbf{Target}                                          & \textbf{Generated}                                                                                                           \\
+        \hline
+        nevermind.
+are you at work?
+& yea                                                      & i'm all alone over here...
+\\
+        \hline
+        what re your plans for tomorrow?
+& drop prentice's car off at shop; go to dome              & leaving early tomorrow.
+leaving early.
+leaving early.
+leaving early.
+\\
+        \hline
+        I just refaxed it.
+For your information, my total hours is 49.
+& I noted your hours..I will look for the t/s Thanks Lisa!
+& Thanks Rick, and let's talk after the holidays about a new game plan...
+Best regards and happy thanksgiving.
+Jaime Williams.
+\\
+        \hline
+    \end{tabularx}
+    \caption{Example of generated replies}
+    \label{table:example-reply-bleu}
+\end{table}
+
+As shown in Table~\ref{table:example-reply-bleu}, BLEU is not a good option for this problem.
+Therefore, a subjective assessment of the replies was made.
+We generated some replies, created a form using Google Forms, and asked some people to answer the questionnaire.
+
+The question asked for each reply generated was: Was this reply generated using Artificial Intelligence software? The interviewee could choose only yes or no.
+
+The form contains only five emails and replies.
+The Table~\ref{table:is-it-ai-test} shows the results of the test answered XXX times.
+The column AI?
+shows the percentage of answers that believed the reply was generated by an AI system.
+The column Correct?
+shows whether what people believed was correct or not.
+
+\begin{table*}[ht]
+    \centering
+    \begin{tabularx}{\textwidth}{|X|X|c|c|}
+        \hline
+        \textbf{Email}                                                                                                                                                                                        & \textbf{Reply}                                                                                                                                                                                                                     & \textbf{AI?} & \textbf{Correct?} \\
+        \hline
+        Let me know if this works.
+& This works great.
+Will let you know.
+as soon as I get a chance, let me know                                                                                                                                                        & \num{0}{\%}  & yes               \\
+        \hline
+        Following are the terms under which I ran the Forward Obligation report and received this message: General SQL error.
+ORA-00907: missing right parenthesis.
+Terms: Let me know what you find.
+Thanks!
+& Kate, I ran the report with the exact same options and it came right up.
+Try it again, exactly as before.
+Usually if it works for one person and not the other it is a security issue.
+Let me know what happens.
+Thanks, Brettther & \num{0}{\%}  & yes               \\
+        \hline
+        Didn't you trade uranium at one time?
+& Yeah, I know the buisness VERY well.
+& \num{0}{\%}  & no                \\
+        \hline
+        Are you free for drinks either Monday or Wednesday?
+& Yes                                                                                                                                                                                                                                & \num{0}{\%}  & no                \\
+        \hline
+        Mons, I would be available on the 25th, 26th or 27th.
+I cannot make it the week of the 18th.
+Thanks, Bill.
+& OK, so, let's see if we can get together later today.
+I have to leave at 16:00 for a few minutes, but I am sure that I will be out at that moment.
+Thank you Kim.
+& \num{0}{\%}  & yes               \\
+        \hline
+    \end{tabularx}
+    \caption{Is it AI? test}
+    \label{table:is-it-ai-test}
+\end{table*}
+
+\todo[inline]{Explain here the results of the form.}
+
+\section{Conclusion}
+
+Despite the small dataset used and limited resources available, the fine-tuned model performed well.
+In a further works, the dataset must be revised to avoid data that may cause noise in the predictions.
 

### 2020-06-27 latex/slides/slides.tex
Rearrange the paper and slides folders
Update paper
Update slides

--- 2020-06-25 slides/slides.tex
@@
 \usepackage[utf8]{inputenc}
-\usepackage{utopia}
 \usepackage{hyperref}
@@
 \usepackage{siunitx}
+\usepackage{todonotes}
 \sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
@@
 
+  {\scriptsize
+    yuck yuck
+    \bigbreak
+    -----Original Message-----
+    \bigbreak
+    har har
+  }
+  \bigbreak
+  \bigbreak
+
+  The subject is: \textbf{Wine tasting}.
+\end{frame}
+
+\begin{frame}
+  \frametitle{The Enron Email Dataset}
+
   \begin{itemize}
@@
   \frametitle{BERT architecture}
+
+  \todo[inline]{Describe here the architecture that the professor showed in the class.}
 \end{frame}
@@
 \begin{frame}
-  \frametitle{Learning Rate Schedule}
+  \frametitle{Learning rate schedule}
 
   \begin{itemize}
-    \item Warm-up steps: \num{10000};
+    \item Warm-up steps: \num{5000};
     \item Learning rate: \num{1e-4};
@@
 
-  \includegraphics[width=\textwidth]{../latex-data/images/warmup_linear_schedule.png}
+  \includegraphics[width=\textwidth]{../images/warmup_linear_schedule.pdf}
 \end{frame}
@@
           \end{itemize}
-    \item Batch size: \num{8};
-    \item Training epochs: \num{32};
+    \item Batch size: \num{10};
+    \item Training epochs: \num{10.5};
     \item Beam search hypothesis: \num{3};
   \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{Loss function}
+
+  \includegraphics[width=\textwidth]{../images/loss_function.pdf}
 \end{frame}
@@
 \begin{frame}
+  \frametitle{BLEU score}
+
+  \begin{itemize}
+    \item <1-> 21 emails in the evaluation dataset;
+    \item <2-> BLEU score = \num{0.0};
+  \end{itemize}
+\end{frame}
+
+\begin{frame}
+  \frametitle{BLEU score}
+
+  \begin{table}
+    \begin{tabularx}{\textwidth}{|X|X|X|}
+      \hline
+      \textbf{Input}                                                  & \textbf{Target}                                          & \textbf{Generated}                                                                                                           \\
+      \hline
+      nevermind.
+are you at work?
+& yea                                                      & i'm all alone over here...
+\\
+      \hline
+      what re your plans for tomorrow?
+& drop prentice's car off at shop; go to dome              & leaving early tomorrow.
+leaving early.
+leaving early.
+leaving early.
+\\
+      \hline
+      I just refaxed it.
+For your information, my total hours is 49.
+& I noted your hours..I will look for the t/s Thanks Lisa!
+& Thanks Rick, and let's talk after the holidays about a new game plan...
+Best regards and happy thanksgiving.
+Jaime Williams.
+\\
+      \hline
+    \end{tabularx}
+  \end{table}
+\end{frame}
+
+\begin{frame}
   \frametitle{Generated replies}
@@
   \begin{table}
-    \centering
-    \begin{tabularx}{\textwidth}{|X|X|c|}
+    \scriptsize
+    \begin{tabularx}{\textwidth}{|X|X|c|c|}
       \hline
-      \textbf{Email}                      & \textbf{Reply}                                                                              & \textbf{AI?} \\
+      \textbf{Email}                                                                                                                                                                                        & \textbf{Reply}                                                                                                                                                                                                                     & \textbf{AI?} & \textbf{Correct?} \\
       \hline
-      Shall we have the meeting tomorrow? & meeting is postponed because the 3 : 00 p. m. meeting today. meeting is canceled for today. & \num{30}{\%} \\
+      Let me know if this works.
+& This works great.
+Will let you know.
+as soon as I get a chance, let me know                                                                                                                                                        & \num{0}{\%}  & yes               \\
       \hline
-      hi                                  & Hi how are you?                                                                             & \num{10}{\%} \\
+      Following are the terms under which I ran the Forward Obligation report and received this message: General SQL error.
+ORA-00907: missing right parenthesis.
+Terms: Let me know what you find.
+Thanks!
+& Kate, I ran the report with the exact same options and it came right up.
+Try it again, exactly as before.
+Usually if it works for one person and not the other it is a security issue.
+Let me know what happens.
+Thanks, Brettther & \num{0}{\%}  & yes               \\
       \hline
-      you look so handsome today          & why thank you, you do as well                                                               & \num{30}{\%} \\
+      Didn't you trade uranium at one time?
+& Yeah, I know the buisness VERY well.
+& \num{0}{\%}  & no                \\
+      \hline
+      Are you free for drinks either Monday or Wednesday?
+& Yes                                                                                                                                                                                                                                & \num{0}{\%}  & no                \\
+      \hline
+      Mons, I would be available on the 25th, 26th or 27th.
+I cannot make it the week of the 18th.
+Thanks, Bill.
+& OK, so, let's see if we can get together later today.
+I have to leave at 16:00 for a few minutes, but I am sure that I will be out at that moment.
+Thank you Kim.
+& \num{0}{\%}  & yes               \\
       \hline
@@
 
+%---------------------------------------------------------
+\section{Miscellaneous}
+
+\begin{frame}
+  \frametitle{Miscellaneous}
+
+  \begin{itemize}
+    \item \href{https://github.com/claudioscheer/seq2seq-bert}{https://github.com/claudioscheer/seq2seq-bert};
+    \item \href{https://github.com/claudioscheer/seq2seq-bert/releases/tag/v0.0.8-alpha}{Final release (v0.0.8)};
+  \end{itemize}
+\end{frame}
+%---------------------------------------------------------
+
 \end{document}

### 2020-06-27 latex/slides/slides.tex
Update slides

@@
 %---------------------------------------------------------
-\section{BERT}
+\section{Implementation}
+
+\begin{frame}
+  \frametitle{Hugging Face}
+
+  \begin{itemize}
+    \item BERT base;
+          \begin{itemize}
+            \item 12 layers;
+          \end{itemize}
+    \item Hugging Face and PyTorch;
+    \item NVIDIA T4 GPU on AWS;
+          \begin{itemize}
+            \item 16GB;
+          \end{itemize}
+  \end{itemize}
+\end{frame}
 
@@
   \todo[inline]{Describe here the architecture that the professor showed in the class.}
-\end{frame}
-
-\begin{frame}
-  \frametitle{Hugging Face}
-
-  \begin{itemize}
-    \item BERT base was used;
-          \begin{itemize}
-            \item 12 layers;
-          \end{itemize}
-    \item Hugging Face and PyTorch was used;
-  \end{itemize}
 \end{frame}
@@
     \item Batch size: \num{10};
-    \item Training epochs: \num{10.5};
+    \item Fine-tuning epochs: \num{10.5};
     \item Beam search hypothesis: \num{3};
@@
       \hline
-      \textbf{Email}                                                                                                                                                                                        & \textbf{Reply}                                                                                                                                                                                                                     & \textbf{AI?} & \textbf{Correct?} \\
+      \textbf{Email}                                                                                                                                                                                        & \textbf{Reply}                                                                                                                                                                                                                     & \textbf{AI?}   & \textbf{Was it AI?} \\
       \hline
@@
 Will let you know.
-as soon as I get a chance, let me know                                                                                                                                                        & \num{0}{\%}  & yes               \\
+as soon as I get a chance, let me know                                                                                                                                                        & \num{100}{\%}  & yes                 \\
       \hline
@@
 Let me know what happens.
-Thanks, Brettther & \num{0}{\%}  & yes               \\
+Thanks, Brettther & \num{50}{\%}   & yes                 \\
       \hline
@@
 & Yeah, I know the buisness VERY well.
-& \num{0}{\%}  & no                \\
+& \num{33.3}{\%} & no                  \\
       \hline
       Are you free for drinks either Monday or Wednesday?
-& Yes                                                                                                                                                                                                                                & \num{0}{\%}  & no                \\
+& Yes                                                                                                                                                                                                                                & \num{66.7}{\%} & no                  \\
       \hline
@@
 Thank you Kim.
-& \num{0}{\%}  & yes               \\
+& \num{16.7}{\%} & yes                 \\
       \hline
@@
     \item \href{https://github.com/claudioscheer/seq2seq-bert/releases/tag/v0.0.8-alpha}{Final release (v0.0.8)};
+    \item \href{https://www.kaggle.com/wcukierski/enron-email-dataset}{The Enron Email Dataset};
+    \item \href{https://www.kaggle.com/claudioscheer/extract-reply-emails}{Dataset parser};
   \end{itemize}

### 2020-06-29 latex/paper/paper.tex
Update paper and slides
Update paper

@@
 \usepackage{hyperref}
-\usepackage{tabularx}
 \usepackage{siunitx}
@@
 \usepackage{todonotes}
+\usepackage{tabularx}
+\usepackage{caption}
+% \usepackage{placeins}
 \sisetup{output-exponent-marker=\ensuremath{\mathrm{e}}}
@@
     /Title (Email Autoresponder using a Sequence-to-sequence Architecture with BERT)
-    /Author (Claudio Scheer, Jos\'e Fernando Possebon)
+    /Author (Claudio Scheer, Jose Fernando Possebon Junior)
 }
 \setcounter{secnumdepth}{0}
+\newcommand{\source}[1]{\caption*{Source: {#1}}}
+\nocopyright
+
 \begin{document}
@@
 \title{Email Autoresponder using a Sequence-to-sequence\\Architecture with BERT}
-\author{Claudio Scheer \and Jos\'e Fernando Possebon\\
+\author{Claudio Scheer \and Jose Fernando Possebon Junior\\
     Pontifical Catholic University of Rio Grande do Sul - PUCRS\\
@@
     \begin{quote}
-        Due to the large number of emails that people receive, it is not just about filtering what is spam or not, but it is also essential to help people filter what requires their attention from something that can be done by an intelligent agent.
-If we consider the scenario of a sales representative who sells software licenses, for example, it is common to receive requests for quotations from their customers about the price of software licenses.
-We believe that it is possible to implement an agent that could read the emails, understand what is requested, and respond to their emails automatically.
+        This paper is related to a practical project of deep learning discipline of Master's in Computer Science of the Pontifical Catholic University of Rio Grande do Sul.
+We considered that emails are a good source of non-structured data, and that are some automation opportunities.
+Therefore, we fine-tuned the BERT model to reply emails in the English language.
+The final model could not be evaluated using a quantitative metric.
+However, a more subjective metric showed that, in general, the model still presents some problems that allow the human being to recognize when an AI system is replying to an email.
     \end{quote}
@@
 
-\noindent Introduction.
+\section{1. Introduction}
 
-\section{Related works}
-Related works.
+If we consider the scenario of a sales representative who sells software licenses, for example, it is common to receive requests for quotations from their customers about the price of software licenses.
+There are some opportunities to provide some automation on this task.
+Therefore, aiming to automate the answering emails task, we implement in this paper an agent that is able to reply an email using a deep learning model.
 
-\section{Deep Learning}
+We can implement this agent with two primary components: one to read the email messages and send the responses and another to receive the email messages parse it and prepare the response based on message content.
+In this paper, we deal with the piece of software responsible for receiving the message content and generate the proper reply for that message.
 
-In this section, we will discuss the sequence-to-sequence model using recurrent neural networks and transformers. In addition, we also discuss how a BERT model works.
+A significant amount of software uses Natural Language Understanding (NLU), and they achieve excellent results in understanding the context of messages and generating a proper response to that.
+Looking for all different approaches that we can use on natural language understanding, dataset availability, and time to implement, we choose to fine-tune a BERT model for the sequence-to-sequence (Seq2Seq) task.
 
-\subsection{Sequence-to-sequence}
+The first idea was to implement something using the Brazilian Portuguese language, and we have looked for some datasets available.
+We could not find any suitable source of data to train our model.
+We know that there are many more datasets in the English language available, so we decide to go that way.
 
-The encoder-decoder architecture was initially proposed by \cite{DBLP:journals/corr/ChoMGBSB14}.
-Although simple, the idea is powerful: use a recurrent neural network to encode the input data and a recurrent neural network to decode the encoded input into the desirable output.
-Two neural networks are trained.
+We did not implement the piece of checking email inbox and sending the answer email. We consider this task; it is trivial, and it is not the objective of this assignment.
 
-\cite{DBLP:journals/corr/Graves13} - Generating sequences with LSTM
+Our goal for this assignment is to provide software capable of receiving any text with some context and producing a meaningful answer to that.
+To make it happen, we will use a public dataset of emails with responses to train our model and do some experiments.
+Later on, we will submit a survey to a group of people asking them to identify based on some questions when the answers were from a human or computer software.
 
-- Attention is all you need
+In the Section~2, we present some the background about the BERT model and the architecture used in this paper.
+Section~5 discusses how we parsed the dataset and the results achieved with the fine-tuned model.
+
+\section{2. Background}
+
+For this assignment, we need to understand concepts about language model, sequence-to-sequence (Seq2Seq), attention mechanisms, and transformers.
+As we saw in classes, when we have a sequence of words, we need to compute the distribution of probabilities of the next word of sequence based on specific vocabulary.
+This system is known as a language model.
+Simply we consider language model as a system that defines probabilities to a piece of text.
+There are some issues with language models based on n-grams: sparse, storage of count of n-grams in memory.
+Another possibility is to use a trigram approach, but we saw that although the result generated is grammatically complaint on the English language, we do not have a context.
+So this is not what we need, and we learned too about sequence-to-sequence (Seq2Seq).
 
@@
 BERT is a short for Bidirectional Encoder Representations from Transformers, proposed by \cite{DBLP:journals/corr/abs-1810-04805}.
-Transformers network was proposed by \cite{DBLP:journals/corr/VaswaniSPUJGKP17} and use the attentions mechanism, proposed by \cite{DBLP:journals/corr/BahdanauCB14}, to learn representations between words that can express their contextual meaning.
+Transformers network was proposed by \cite{DBLP:journals/corr/VaswaniSPUJGKP17} and use the attention mechanism, proposed by \cite{DBLP:journals/corr/BahdanauCB14}.
+In a nutshell, the attention mechanism can learn representations between words that express their contextual meaning.
+
+Since BERT is bidirectional, the attention mechanism does not learn only representations of just the previous words, but for all the words in the sentence.
+To achieve this, BERT was pre-trained for masked language modeling and next sentence predictions tasks.
+However, with the adjustment of the output layers and a fine-tuning process, the model can be used for other tasks, using the same parameters as the original BERT model.
 
 The original BERT model was pre-trained in a corpus comprising Wikipedia and Book Corpus.
-BERT has two pre-trained models available: BERT large, with \num{345}{M} parameters (24 layers) and BERT base, with \num{110}{M} (12 layers).
+Two pre-trained models are available: BERT large, with \num{345}{M} parameters and 24 layers, and BERT base, with \num{110}{M} and 12 layers.
 
-The model was pre-trained for masked language modeling nas next sentence predictions tasks.
-However, with the replacement of the last layer and fine-tuning, the model can be used for other tasks, using the same parameters as the original BERT model.
+Figure~\ref{fig:transformer} shows the architecture of a Transformer network, proposed by \cite{DBLP:journals/corr/VaswaniSPUJGKP17}.
+Originally, Transformers was proposed to be used for machine translation tasks, so the architecture has encoder and decoder blocks.
+BERT uses this same architecture, but trained with different tasks, as previously stated.
 
-discuss it here
+The next two sections discusses the BERT model encoder and decoder blocks, used for sequence-to-sequence tasks.
 
-In a nutshell, the difference is that self-attention is only applied to the input sequence, while cross-attention is applied to the input and output sentences.
+\begin{figure}[ht]
+    \centering
+    \includegraphics[width=0.47\textwidth]{../images/transformer_architecture.png}
+    \caption{Transformer Architecture}
+    \label{fig:transformer}
+    \source{\cite{DBLP:journals/corr/VaswaniSPUJGKP17}}
+\end{figure}
 
-\section{Dataset}
+\subsection{BERT encoder}
+
+In the first step, each token in the sequence is embedded in a $N$ dimmensions vector.
+The position of the token in the sentence is also taken into account.
+Therefore, after embedding the tokens, positional encoding is added to the embedded matrix.
+In BERT, the embedding and the position encoding is learned through back-propagation.
+
+The next block in Figure~\ref{fig:transformer} is the encodding block.
+This block can be chained $n$ times to, intuitively, learn more complex relationships between words.
+The BERT base architecture chains 12 of these blocks.
+
+\subsection{BERT decoder}
+
+The embedding of the the decoder block is similar to the encoder block. The difference is that the target sentence is shifted with a token to indicate the start and the end of the sentence.
+
+The masked self-attention used in the decoder ignores the words on the right.
+That is, since the task used in the original Transformer is a language model, the words on the right represents the word that the model needs to learn to predict and should be ignored.
+This is not true for BERT, as it uses different tasks to train the model.
+
+For BERT, the decoder architecture is almost the same as the encoder architecture. The difference is that, for multi-head attention, the output of the encoder network is used.
+
+% \href{https://medium.com/dissecting-bert/dissecting-bert-part2-335ff2ed9c73}{https://medium.com/dissecting-bert/dissecting-bert-part2-335ff2ed9c73}
+
+% \href{https://medium.com/dissecting-bert/dissecting-bert-part-1-d3c3d495cdb3}{https://medium.com/dissecting-bert/dissecting-bert-part-1-d3c3d495cdb3}
+
+% \href{https://medium.com/dissecting-bert/dissecting-bert-appendix-the-decoder-3b86f66b0e5f}{https://medium.com/dissecting-bert/dissecting-bert-appendix-the-decoder-3b86f66b0e5f}
+
+\section{3. Related work}
+
+We know that there is plenty of work done in this area, so we looked at what others already implemented to have insights and technical information on how to achieve our goal.
+At first glance, we checked some features implemented by Google on their email service and what theoretical foundations they used.
+On of the existing features available at Gmail is the Smart Reply that it is an automated response suggestion that users can choose just taping on the suggested text.
+The concept of Smart Reply is to generate a short reply message looking at the context of the email[cite].
+This concept is a good start, but we intend to provide a more detailed answer to our emails.
+[cite] proposes a different approach to answer generation that it is more aligned with what we intend to achieve.
+Although the method used seems to be more efficient, we decided to pursue a more straightforward implementation due to our constraints of datasets, computational resources, and time.
+
+\section{4. Experiments and Results}
+
+In this section, we discuss the how the dataset and the implementation of the sequence-to-sequence model was handled and the results achieved.
+
+\subsection{Dataset}
 
@@
 
-\section{Implementation}
+\subsection{Implementation}
 
@@
 A checkpoint of the model was saved every \num{20000} steps, mitigating the loss of processment if the instance was suddenly stopped.
-The instance was equipped with a 16 GB NVIDIA T4 GPU (CUDA 10.2).
+The instance was equipped with a NVIDIA T4 GPU (CUDA \num{10.2}), with \num{16}{GB} of memory.
 
@@
 
-\section{Results}
+\subsection{Results}
+
+% \FloatBarrier
+\begin{table*}[ht]
+    \centering
+    \begin{tabularx}{\textwidth}{|X|X|c|c|}
+        \hline
+        \textbf{Email} & \textbf{Reply} & \textbf{AI?} & \textbf{Was it AI?} \\
+        \hline
+        Let me know if this works. & This works great. Will let you know. as soon as I get a chance, let me know & \num{95.7}{\%} & yes \\
+        \hline
+        Following are the terms under which I ran the Forward Obligation report and received this message: General SQL error.
+ORA-00907: missing right parenthesis.
+Terms: Let me know what you find.
+Thanks!
+& Kate, I ran the report with the exact same options and it came right up.
+Try it again, exactly as before.
+Usually if it works for one person and not the other it is a security issue.
+Let me know what happens.
+Thanks, Brettther & \num{52.2}{\%} & yes \\
+        \hline
+        Didn't you trade uranium at one time? & Yeah, I know the buisness VERY well. & \num{30.4}{\%} & no \\
+        \hline
+        Are you free for drinks either Monday or Wednesday? & Yes & \num{69.6}{\%} & no \\
+        \hline
+        Mons, I would be available on the 25th, 26th or 27th.
+I cannot make it the week of the 18th.
+Thanks, Bill.
+& OK, so, let's see if we can get together later today.
+I have to leave at 16:00 for a few minutes, but I am sure that I will be out at that moment.
+Thank you Kim.
+& \num{39.1}{\%} & yes \\
+        \hline
+    \end{tabularx}
+    \caption{Is it AI? test}
+    \label{table:is-it-ai-test}
+\end{table*}
+% \FloatBarrier
 
@@
         \hline
-        nevermind.
-are you at work?
-& yea                                                      & i'm all alone over here...
-\\
+        nevermind.  are you at work? & yea & i'm all alone over here... \\
         \hline
-        what re your plans for tomorrow?
-& drop prentice's car off at shop; go to dome              & leaving early tomorrow.
-leaving early.
-leaving early.
-leaving early.
-\\
+        what re your plans for tomorrow? & drop prentice's car off at shop; go to dome              & leaving early tomorrow. leaving early. leaving early. leaving early. \\
         \hline
@@
 
-The question asked for each reply generated was: Was this reply generated using Artificial Intelligence software? The interviewee could choose only yes or no.
+The question asked for each reply generated was: Was this reply generated using Artificial Intelligence software?
+The interviewee could choose only yes or no.
+The form contains only five emails and replies.
+The Table~\ref{table:is-it-ai-test} shows the results of the test answered by 23 human beings.
+The column `AI?' shows the percentage of answers that believed the reply was generated by an AI system.
+The column `Was it AI?' shows whether the reply was generated by an AI system or not.
 
-The form contains only five emails and replies.
-The Table~\ref{table:is-it-ai-test} shows the results of the test answered XXX times.
-The column AI?
-shows the percentage of answers that believed the reply was generated by an AI system.
-The column Correct?
-shows whether what people believed was correct or not.
+In general, Table~\ref{table:is-it-ai-test} shows that human beings can identify that the reply was generated by an AI system.
+Also, it is important to note that when the reply is short, most people think that it is generated by an AI system.
 
-\begin{table*}[ht]
-    \centering
-    \begin{tabularx}{\textwidth}{|X|X|c|c|}
-        \hline
-        \textbf{Email}                                                                                                                                                                                        & \textbf{Reply}                                                                                                                                                                                                                     & \textbf{AI?} & \textbf{Correct?} \\
-        \hline
-        Let me know if this works.
-& This works great.
-Will let you know.
-as soon as I get a chance, let me know                                                                                                                                                        & \num{0}{\%}  & yes               \\
-        \hline
-        Following are the terms under which I ran the Forward Obligation report and received this message: General SQL error.
-ORA-00907: missing right parenthesis.
-Terms: Let me know what you find.
-Thanks!
-& Kate, I ran the report with the exact same options and it came right up.
-Try it again, exactly as before.
-Usually if it works for one person and not the other it is a security issue.
-Let me know what happens.
-Thanks, Brettther & \num{0}{\%}  & yes               \\
-        \hline
-        Didn't you trade uranium at one time?
-& Yeah, I know the buisness VERY well.
-& \num{0}{\%}  & no                \\
-        \hline
-        Are you free for drinks either Monday or Wednesday?
-& Yes                                                                                                                                                                                                                                & \num{0}{\%}  & no                \\
-        \hline
-        Mons, I would be available on the 25th, 26th or 27th.
-I cannot make it the week of the 18th.
-Thanks, Bill.
-& OK, so, let's see if we can get together later today.
-I have to leave at 16:00 for a few minutes, but I am sure that I will be out at that moment.
-Thank you Kim.
-& \num{0}{\%}  & yes               \\
-        \hline
-    \end{tabularx}
-    \caption{Is it AI? test}
-    \label{table:is-it-ai-test}
-\end{table*}
-
-\todo[inline]{Explain here the results of the form.}
-
-\section{Conclusion}
+\section{5. Final Remarks and Future Work}
 
